---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# musePHI


<!-- badges: start -->
[![R-CMD-check](https://github.com/overdodactyl/musePHI/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/overdodactyl/musePHI/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`musePHI` is a package designed to assist in the de-identification of MUSE ECG XML files. It enables users to replace sensitive patient information within XML files with placeholders, maintaining the overall structure of the files. This approach helps in ensuring patient privacy while allowing the data to be used for research or analysis purposes.

## Disclaimer

It is the responsibility of the user to accurately identify and replace values that need to be de-identified from the XML file. Furthermore, users must validate the results to ensure no personal health information (PHI) is inadvertently disclosed. The developers of `musePHI` assume no liability for the misuse of this software or the inadvertent sharing of PHI.


## Installation

You can install the development version of musePHI from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("overdodactyl/musePHI")
```

## Example

```{r example}
library(musePHI)
```

Define the elements you wish to replace in the MUSE XML file:

```{r}
replace <- list(
  "PatientDemographics/PatientLastName" = "LastName",
  "PatientDemographics/PatientFirstName" = "FirstName",
  "PatientDemographics/PatientID" = "PatientID",
  "TestDemographics/AcquisitionDate" = "01-01-0001",
  "TestDemographics/AcquisitionTime" = "00:00:00"
)
```

For each element in the list, the name  should be the path to an XML node (relative to `RestingECG`). The value is what the node will be replaced with. 


Specify the path to your existing XML file and the path for the new de-identified XML file. Then, call muse_deidentify:

```{r}
file <- muse_example("muse/muse_ecg1.xml")
output_file <- tempfile(fileext = ".xml")
muse_deidentify(file, output_file, replace)
```

**NOTE:** It's recommended to save the de-identified ECG data to a new file to preserve the original data.

## Parallelization 

For users working with a large number of XML files, parallelization can significantly speed up the de-identification process. We recommend using the [furrr](https://furrr.futureverse.org) package to efficiently parallelize your workload.


